Target Markdown

### 2024-04-06 _targets.Rmd
Update manuscript and supplementary material

```{targets}
list(
  tar_target(sim_param_file, here::here("data", "sim_param_csc_rerun"), format = "file"),
  tar_target(sim_param, {readRDS(sim_param_file)}),
  tar_target(sim_param_tab,
    sim_param %>%
      mutate(resp_div = 1 - rho) %>%
      select(-A) %>%
      pivot_longer(everything(), names_to = "Parameter", values_to = "values") %>%
      group_by(Parameter) %>%
      summarise(
        u = list(sort(unique(values))),
        n = length(unique(round(values, 2))),
        min = min(values),
        max = max(values)
        )
    ),
  tar_target(tab_sim_param,
    sim_param_tab %>%
      mutate(Values = pmap_chr(list(u = u, min = min, max = max, n = n),
          function(u, min, max, n) {
            if (length(u) < 10) {
              out <- paste0("[", paste(round(u, 2), collapse = ", "), "]")
            } else {
              out <- paste0("(", round(min, 2), ", ", round(max, 2), ")", ", N = ", n)
            }
            out
          }
          )) %>%
      filter(!Parameter %in% c("sim_id", "fw_id", "rho")) %>%
      select(Parameter, Values) %>%
      mutate(Parameter = recode_factor(Parameter, !!!var_replacement()))
  ),
  tar_target(fix_parameter,
    tibble(
      c = 0,
      B0 = 0.5,
      r = 1.0,
      K = 10,
      alpha_ij = 0.5,
      prod_mass = 1.0
    )
  ),
  tar_target(allometric_parameter,
    tibble(
      d0 = 0.4,
      allo_slope = -0.25,
      ax = list(c(producer = 0, ectotherm = 0.88)), #, endotherm = 0.314
      ay = list(c(producer = 0.0, ectotherm = 4.0)), #, endotherm = 8.0 #not allometric
      eij = list(c(carnivory = 0.85, herbivory = 0.45))
    )
  ),
  tar_target(param_table,
    fix_parameter %>%
      bind_cols(allometric_parameter) %>%
      mutate(across(where(is.list), ~map_chr(.x, function(x) paste_named_vector(x)))) %>%
      mutate(across(where(is.double), ~as.character(.x))) %>%
      pivot_longer(everything(), names_to = "Parameter", values_to = "Values") %>%
      mutate(
        Parameter = latex_symbol_replacement()[Parameter],
        Parameter = surround_latex_math(Parameter)
      ) %>%
      bind_rows(tab_sim_param)
  )
)
```

@@

```{r}
tar_load(sim_param_tab)
tar_load(tab_sim_param)
tar_load(param_table)
kable(param_table, "html", booktabs = T, escape = FALSE) %>%
  kable_styling()
```

>>>>

```{r, eval = FALSE}
tar_load(sim_param)
```

```{targets}
list(
  tar_target(sim_param_file, here::here("data", "sim_param_csc_rerun"), format = "file"),
  tar_target(sim_param, {readRDS(sim_param_file)}),
  tar_target(param_comb_nb,
    sim_param %>%
      group_by(Z, rho, env_stoch, c, S) %>%
      summarise(n = n())
  ),
  tar_target(sim_param_tab,
    sim_param %>%
      mutate(resp_div = 1 - rho) %>%
      select(-A) %>%
      pivot_longer(everything(), names_to = "Parameter", values_to = "values") %>%
      group_by(Parameter) %>%
      summarise(
        u = list(sort(unique(values))),
        n = length(unique(round(values, 2))),
        min = min(values),
        max = max(values)
        )
    ),
  tar_target(tab_sim_param,
    sim_param_tab %>%
      mutate(Values = pmap_chr(list(u = u, min = min, max = max, n = n),
          function(u, min, max, n) {
            if (length(u) < 10) {
              out <- paste0("[", paste(round(u, 2), collapse = ", "), "]")
            } else {
              out <- paste0("(", round(min, 2), ", ", round(max, 2), ")", ", N = ", n)
            }
            out
          }
          )) %>%
      filter(!Parameter %in% c("sim_id", "fw_id", "rho", "rep")) %>%
      select(Parameter, Values) %>%
      mutate(
        parameter_name = parameter_name_replacement()[Parameter],
        Parameter = latex_symbol_replacement()[Parameter],
        Parameter = paste0(parameter_name, " (", surround_latex_math(Parameter), ")")
        ) %>%
      select(-parameter_name)
  ),
  tar_target(fix_parameter,
    tibble(
      h = 2,
      B0 = 0.5,
      r = 1.0,
      K = 10,
      alpha_ij = 0.5,
      prod_mass = 1.0
    )
  ),
  tar_target(allometric_parameter,
    tibble(
      d0 = 0.4,
      allo_slope = -0.25,
      ax = list(c(producer = 0, ectotherm = 0.88)), #, endotherm = 0.314
      ay = list(c(producer = 0.0, ectotherm = 4.0)), #, endotherm = 8.0 #not allometric
      eij = list(c(carnivory = 0.85, herbivory = 0.45))
    )
  ),
  tar_target(param_table,
    fix_parameter %>%
  bind_cols(allometric_parameter) %>%
  mutate(across(where(is.list), ~map_chr(.x, function(x) paste_named_vector(x)))) %>%
  mutate(across(where(is.double), ~as.character(.x))) %>%
  pivot_longer(everything(), names_to = "Parameter", values_to = "Values") %>%
  mutate(
    parameter_name = parameter_name_replacement()[Parameter],
    Parameter = latex_symbol_replacement()[Parameter],
    Parameter = paste0(parameter_name, " (", surround_latex_math(Parameter), ")")
    ) %>%
  select(-parameter_name) %>%
  bind_rows(tab_sim_param)
  )
)
```

```{r}

@@

```{r}
tar_load(sim_param_tab)
tar_load(sim_param)
tar_load(tab_sim_param)
tar_load(param_table)
kable(param_table, "html", booktabs = T, escape = FALSE) %>%
  kable_styling()
tar_load(c(fix_parameter, allometric_parameter, tab_sim_param))
ti <- fix_parameter %>%
  bind_cols(allometric_parameter) %>%
  mutate(across(where(is.list), ~map_chr(.x, function(x) paste_named_vector(x)))) %>%
  mutate(across(where(is.double), ~as.character(.x))) %>%
  pivot_longer(everything(), names_to = "Parameter", values_to = "Values") %>%
  mutate(
    parameter_name = parameter_name_replacement()[Parameter],
    Parameter = latex_symbol_replacement()[Parameter],
    Parameter = paste0(parameter_name, " (", surround_latex_math(Parameter), ")")
    ) %>%
  select(-parameter_name) %>%
  bind_rows(tab_sim_param)
ti %>%
  kable("html", booktabs = T, escape = FALSE) %>%
  kable_styling()
```
